\section{Requirements Analysis}
Having analysed available literature on the design of asynchronous, limit order book markets in \Cref{Chapters/Background/Market-Microstructure}, as well as existing Agent-Based ASMs in \Cref{Chapters/Background/Agent-Based-Modelling}, we will now list the requirements that the trading simulator needs to satisfy.

Requirements are prioritised according to the MoSCoW approach:

\begin{itemize}
\item M - Must - These requirements are the highest priority must be completed to ensure project success.
\item S - Should - These requirements are high priority and will be completed after the M requirements.
\item C - Could - These requirements will be worked on only if there is time after the M and S requirements or if they do not interfere with the progress of the higher priority tasks.
\item W - Would - These requirements most probably will not be done and are not necessary for the completion and success of the project but are good ideas for future work.
\end{itemize}

\subsection{Functional Requirements}
\begin{center}
\begin{longtable}[htbp]{c p{4.2in} c }

\multicolumn{1}{c}{\textbf{ID}}           &
\multicolumn{1}{c}{\textbf{Requirement}}  &
\multicolumn{1}{c}{\textbf{Priority}}     \\              
\toprule

\multicolumn{3}{c}{\textbf{Market Agent}}   	         \\
F01  & The Market Agent shall match orders on the limit order book & M \\ 
F02  & The Market Agent shall accept limit/market orders and order cancellations. & M \\
F03  & The Market Agent shall provide \textit{level 2} market data access with anonymous order ids. & M \\
F04  & The Market Agent shall report order executions and status changes back to the order owner. & M \\ 

\multicolumn{3}{c}{\textbf{Simulation Agent}}   \\
F05  & The Simulation Agent shall start all specified agents.  & M \\
F06  & The Simulation Agent shall synchronise the start of a simulation. & M \\
F07  & The Simulation Agent shall stop a simulation after a specified amount of time. & M \\
F09  & The Simulation Agent shall bootstrap the limit order book before starting the simulation. & M \\ 

\multicolumn{3}{c}{\textbf{Client API}}   \\
F10  & The Client API shall handle the low-level interaction with the Market Agent and Simulation Agent and provide callback methods for receiving messages. & M \\

\multicolumn{3}{c}{\textbf{Other}}   		             \\
F11  & The System shall log all events to a file.        & M \\
         
\end{longtable}
\end{center}

\needspace{30\baselineskip}
\subsection{Non Functional Requirements}
\begin{table}[htbp]
\begin{center}
\begin{longtable}{c p{4.2in} c }

\multicolumn{1}{c}{\textbf{ID}}           &
\multicolumn{1}{c}{\textbf{Requirement}}  &
\multicolumn{1}{c}{\textbf{Priority}}     \\        
\toprule

N01  & The System shall handle incoming order rate of              & M \\ 
N02  & The System shall maintain $\geq70\%$ unit test coverage.    & M \\
N03  & The System shall be highly modular and decoupled.           & M \\
N04  & The System shall be integration tested.	                   & M \\
N05  & The System shall imitate the message types and formats of industry standard messaging formats. & M \\
N06  & The System shall publish performance statistics at runtime. & C \\

         
\end{longtable}
\end{center}
\end{table}

