\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}

\parindent=1in

\usepackage[T1]{fontenc}

\usepackage{booktabs}
\usepackage{longtable}

\usepackage{listings}
\lstset{language=Java, numbers=left, frame=single}

\usepackage{color}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{caption}
\usepackage{float}
\usepackage{graphicx}

\usepackage{hyperref}

\usepackage{multirow}

\title{Eugene: Agent-Based Market Simulator for use in System Testing of Trading Algorithms}
\author{Jakub Kozlowski \and Internal Supervisor: Dr. Christopher D. Clack \and External Supervisor: Ian Rose-Miller, UBS}
\date{\today}

\begin{document}

\maketitle

\section*{Aim}
To determine the efficacy of the Agent-Based Market Simulation approach for use in System Testing of Trading Algorithms.

\section*{Objectives}
\begin{itemize}
\item Analyse existing Agent-Based approaches to Market Simulation to determine a set of possible Agent Types that will simulate different trading behaviours.
\item Implement the Agents and their environment (Stock Market Agent, post-simulation Statistical Engine).
\item Discover a specific configuration of Agents whose behaviour will simulate a particular day of trading, in regards to a benchmark.
\item Evaluate the success of the simulator by comparing the emergent behaviour to the benchmark, as well running the simulation against a Trading Algorithm and analysing its behaviour.
\end{itemize}

\section*{Deliverables}
\begin{itemize}
\item A fully functional and tested implementation of Eugene with a design specification.
\item A realistic simulation of a particular day of trading, in regards to a benchmark.
\item Results and analysis from running the Eugene simulation against a Trading Algorithm.
\item A strategy for connecting Eugene to a FIX engine, like \texttt{quickfixj}.
\end{itemize}

\section*{Work Plan}
\begin{tabular}{ p{1.6in} p{3in} }

        \toprule
        
        \multicolumn{1}{l}{\textbf{Dates}}                               		 &
        \multicolumn{1}{l}{\textbf{Description}}                                \\
        
        7\textsuperscript{th} Nov - 18\textsuperscript{th} Dec 2011 &
        
        \begin{itemize}
        \item Market Agent with Market Feed.
        \item Market Agent Performance Tests.
        \item Random Trader Agent.
        \item Simulation lifecycle management.
        \item Post-simulation analysis engine.
        \item Complete end-to-end simulation.
        \end{itemize}                             \\

        19\textsuperscript{th} Dec 2011 - 19\textsuperscript{th} Feb 2012 &
        \begin{itemize}
        \item Implement Agents.
        \item Interim Report.
        \item Run Simulations and compare against benchmark.
        \end{itemize}
        \\
        
        20\textsuperscript{th} Feb 2012 - 27\textsuperscript{th} April 2012 &
        \begin{itemize}
        \item Thesis.
        \item Running simulations against a Trading Algorithm.
        \end{itemize}
        \\
        
        \bottomrule
        
        \\[1in]
        
\end{tabular}

\begin{flushright}
Supervisor's Signature\hspace{0.5cm} \makebox[1.5in]{\hrulefill}
\end{flushright}
\end{document}